\Large{ Authors' reply to the comments by Anonymous Referee (Referee \#2) of the manuscript gmd-2017-119} \\ \LARGE \textbf{Plume-SPH 1.0: A three-dimensional, dusty-gas volcanic plume model based on smoothed particle hydrodynamics}

### 2018-03-21 Reply-to-RC2.tex
Final Response, Figures

\maketitle
The comments by the reviewer are recited in italics, followed by our reply in upright font. Equation, section, and figure numbers   in our response are corresponding to these in the original 
version of GMD discussion paper. \\[12pt]

@@

Thanks for pointing out some of the more recent work on volcanic plume modeling. 
Work by \citet{costa2018understanding} motivates the development of more comprehensive 3D computational models like those in this paper. Reading this paper has inspired new application ideas for Plume-SPH. Citation of this paper is added in "Introduction" section to emphasize the advantage of developing more comprehensive plume model based on SPH.

We have considered coupling a volcanic plume model with a magma reservoir model. It is critical for any plume simulation to use more accurate eruption conditions, which might be obtained from a magma reservoir model. Thank you for pointing out the new degassing model to infer magma dynamics in volcanic plumes \cite{terray2018new}. Comments regarding coupling volcanic plume model with magma reservoir model are added in conclusion section of this paper along with proper citation.
\\[3pt]

@@

Without accounting for the detailed algorithm, the complexity for raw SPH method is $O(N*N)$ operations. Where, $N$ is the total number of particles (SPH particles are essentially equivalent to discretization points  in mesh-based methods). By adopting a background mesh and a compact-supported kernel function, the  complexity will be reduced to $O(MN+mN)$. Where $m$ is the average of number of particles within the compact support of the kernel function, $M$ is number of particles among which neighbor searches are carried out. Please note that number of particles within the compact support of the kernel function is not constant in our case.

@@

To address your questions and clean up confusion, we made a major revision in section 3.10 (is section 3.9 in the revised manuscript). In addition, portion of our response to reviewer's second comments are also added in section 3.10.

@@

Here is a summary on major adjustments made in the revised manuscript: 
Major revision is made in "Parallelism and performance" section (section 3.10 in original manuscript and 3.9 in the revised manuscript). 
\begin{thebibliography}{3}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

>>>>

\maketitle
The comments by the reviewer are recited in italics, followed by our reply in upright font. Revision are highlighted with blue. Equation, section, and figure numbers   in our response are corresponding to these in the original 
version of GMD discussion paper. \\[12pt]

@@

Thanks for pointing out some of the more recent work on volcanic plume modeling. 
Work by \citet{costa2018understanding} motivates the development of more comprehensive 3D computational models like those in this paper. Reading this paper has inspired new application ideas for Plume-SPH. {\color{blue} Citation of this paper is added in "Introduction" section} to emphasize the advantage of developing more comprehensive plume model based on SPH.

We have considered coupling a volcanic plume model with a magma reservoir model. It is critical for any plume simulation to use more accurate eruption conditions, which might be obtained from a magma reservoir model. Thank you for pointing out the new degassing model to infer magma dynamics in volcanic plumes \cite{terray2018new}. {\color{blue}Comments regarding coupling volcanic plume model with magma reservoir model are added in conclusion section of this paper along with proper citation.}
\\[3pt]

@@

Without accounting for the detailed algorithm, the complexity for raw SPH method is $O(N*N)$ operations. Where, $N$ is the total number of particles (SPH particles are essentially equivalent to discretization points  in mesh-based methods). By adopting a background mesh and a compact-supported kernel function, the  complexity will be reduced to $O(MN+mN)$. Where $m$ is the average of number of particles within the compact support of the kernel function, $M$ is number of particles among which neighbor searches are carried out. Please note that number of particles within the compact support of the kernel function is not constant in our case. {\color{blue} Basic analysis on time complexity is added in section ``Parallellism and Performance".}

@@

To address your questions and clean up confusion, {\color{blue}we made a major revision in section 3.10 (is section 3.9 in the revised manuscript). In addition, portion of our response to reviewer's second comments are also added in section 3.10.}

@@

{\color{blue}Here is a summary on major adjustments made in the revised manuscript: 
Major revision is made in "Parallelism and performance" section (section 3.10 in original manuscript and 3.9 in the revised manuscript).}

\begin{thebibliography}{3}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
